On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-08-16 manuscripts/PNAS/chazthm_pnas.tex
chaz

We remark that these results have a surprising application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of compressive communication between sparsely active neural populations \cite{Isely10}.

\begin{proposition}
Random noisy (linear) compression of sparse neural activities is decodable by any neurally-plausible unsupervised sparse (linear) feature learning algorithm that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt} (e.g. \cite{rehnsommer2007, rozell2007neurally}).
\end{proposition}
%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}

>>>>

We remark that these results have an important application to theoretical neuroscience by mathematically justifying one of the few hypothesized theories of bottleneck communication between sparsely active neural populations \cite{Isely10}.

\begin{proposition}
Sparse neural population activity is recoverable from random (linear) noisy compression by any method that solves Prob.~\ref{DeterministicUniquenessTheorem} or \ref{SLCopt}; in particular, via biophysically plausible unsupervised sparse coding (e.g. \cite{rehnsommer2007, rozell2007neurally}).
\end{proposition}
%\cite{rehnsommer2007, rozell2007neurally, ganguli2012compressed, hu2014hebbian}
